---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse=TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# arcadiathemeR

The goal of the arcadiathemeR package is to create ggplot2-style plots in R that (mostly) adhere to Arcadia Science style guidelines.

## Installation
You can install arcadiathemeR from Github using the `remotes` package. If you do not have this package installed you will need to do so before installing the `arcadiathemeR` package.
```r
# install.packages("remotes")
remotes::install_github("Arcadia-Science/arcadiathemeR")
```

## Usage
See the full vignette (TBD)

To access the functions in the arcadiathemeR package, load with: 
```r
library(arcadiathemeR)
```

The arcadiathemeR package is modeled after the [`ggthemes` package](https://github.com/jrnold/ggthemes), layering on the plot theme and color palettes in the same fashion as the `ggthemes` package. 

```{r, base_use}
library(ggplot2)
library(arcadiathemeR)

ggplot(data=mtcars, aes(x=hp, y=mpg, color=as.factor(cyl))) +
  geom_point(size=2.5) +
  theme_arcadia() +
  scale_color_arcadia("accent")
```

You can also select different indices of colors from the palettes within the `scale` function:

```{r, scale_index}
ggplot(mtcars, aes(x = hp, fill = as.factor(cyl))) +
  geom_density(alpha = 0.8) +
  theme_arcadia() +
  scale_fill_arcadia("accent_expanded", start=2, end=5)

```

## Development
To install the package locally while in development, follow the instructions [here](https://stackoverflow.com/questions/21171142/how-to-install-r-package-from-private-repo-using-devtools-install-github). Briefly: 

1. Add a `.Renviron` file to the folder where you are going to install this package
2. Create a Github personal access token, select "repo" to access private repositories 
3. Save the token in the `.Renviron` file as `GITHUBTOKEN=<string>`
4. Install from a specific branch with: 
```r
remotes::install_github("Arcadia-Science/arcadiathemeR", \
ref="EAM/sysfonts", \
auth_token=Sys.getenv("GITHUBTOKEN"))
```
