---
output: github_document
---

```{r, echo = FALSE, warning= FALSE}
knitr::opts_chunk$set(
  collapse=TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# arcadiathemeR

The goal of the arcadiathemeR package is to create ggplot2-style plots in R that (mostly) adhere to Arcadia Science style guidelines.

## Installation
You can install arcadiathemeR from Github using the `remotes` package. If you do not have this package installed you will need to do so before installing the `arcadiathemeR` package.
```r
# install.packages("remotes")
remotes::install_github("Arcadia-Science/arcadiathemeR")
```

To use the custom fonts you need to download the `TTF` formatted font files and place in the `Users/YOURUSERNAME/Library/Fonts/` directory. You can also download the fonts and double click on them to install using FontBook with Mac OS. Check out the Arcadia Science Brand Assets page in Notion to find these. This should only need to be performed once even if the package is updated over time. These steps and functionality have only been confirmed to work on Mac OS.

## Usage
To access the functions in the arcadiathemeR package, load with: 
```r
library(arcadiathemeR)
```

The arcadiathemeR package is modeled after the [`ggthemes` package](https://github.com/jrnold/ggthemes), layering on the plot theme and color palettes in the same fashion as the `ggthemes` package. 

```{r, base_use}
library(ggplot2)
library(arcadiathemeR)

ggplot(data=mtcars, aes(x=hp, y=mpg, color=as.factor(cyl))) +
  geom_point(size=2.5) +
  theme_arcadia(x_axis_type = "numerical") +
  scale_color_arcadia(palette_name = "primary")
```

By default the `theme_arcadia()` function assumes that both axes are numerical data. Since we have different font and plot styles for categorical data, you can specify if the axis is categorical with: 

```{r, categorical_plot}
ggplot(data=diamonds, aes(x=cut, fill=cut)) +
  geom_bar() +
  theme_arcadia(x_axis_type = "categorical") +
  scale_fill_arcadia(palette_name = "secondary", reverse = TRUE) +
  scale_y_continuous(expand=c(0,0)) + # removes whitespace between axis and bars
  theme(legend.position = "bottom")
```


To save plots, we have a custom `save_arcadia_plot()` function built on top of `ggsave()` that helps you export plots that adhere to our size guidelines and can be used with the Illustrator templates. The different plot size options are `"full_wide", "float_wide", "half_square", "full_square",` or `"float_square"`. Additionally for the background to be transparent in exported plots you need to set this argument to `FALSE` in the `theme_arcadia()` function:
```{r, export_plot}
plot <- ggplot(data=diamonds, aes(x=cut, fill=cut)) +
  geom_bar() +
  theme_arcadia(x_axis_type = "categorical", background = FALSE) +
  scale_fill_arcadia(palette_name = "secondary", reverse = TRUE) +
  scale_y_continuous(expand=c(0,0)) + # removes whitespace between axis and bars
  theme(legend.position = "bottom")

save_arcadia_plot("man/figures/arcadia-plot.pdf", plot, panel_size = "full_square")

```

You can also select different indices of colors from the palettes within the `scale` function:

```{r, scale_index}
ggplot(mtcars, aes(x = hp, fill = as.factor(cyl))) +
  geom_density(alpha = 0.8, linewidth = 0) + # remove border line from filled-in density plots
  theme_arcadia() +
  scale_fill_arcadia(palette_name = "blue_shades", start=2, end=5) +
  scale_y_continuous(expand=c(0,0)) +
  scale_x_continuous(expand=c(0,0)) # remove whitespace between both axes and the plot
```


You can also apply gradient palettes to your plots with `gradient_fill_arcadia` or `gradient_scale_arcadia` in a similar fashion to the above: 
```{r, gradient_example}
ggplot(data = mtcars, aes(x = hp, y = mpg, color = hp)) +
 geom_point(size=2.5) + 
 theme_arcadia() + 
 gradient_color_arcadia(palette_name = "lisafrank")

```

There are also bicolor gradients available that are useful for heatmap plots, and you can also remove the background color with `background = FALSE` in the `theme_arcadia()` function: 
```{r, heatmap_example, warning=FALSE}
library(reshape2)

# heatmap of correlation matrix from iris dataset
data(iris)
iris_data <- iris[, 1:4]
cor_matrix <- cor(iris_data)
melted_cor_matrix <- (melt(cor_matrix))

ggplot(melted_cor_matrix, aes(x=Var1, y=Var2, fill=value)) +
  geom_tile() +
  theme_arcadia(x_axis_type = "categorical", y_axis_type = "categorical", background = FALSE) +
  gradient_fill_arcadia(palette_name = "reds") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "top") +
  labs(x = "", y = "")

```

You can view all the color palette options and the individual hex codes composing each palette within the main and gradient palettes with:
```{r}
show_arcadia_palettes()
show_arcadia_gradients()
```

## Development
To install the package locally from a specific branch while in development, do the following:

```r
# TODO change to main once deployed
remotes::install_github("Arcadia-Science/arcadiathemeR", \
ref="EAM/embed-fonts"
```
