---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse=TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# arcadiathemeR

The goal of the arcadiathemeR package is to create ggplot2-style plots in R that (mostly) adhere to Arcadia Science style guidelines.

## Installation
You can install arcadiathemeR from Github using the `remotes` package. If you do not have this package installed you will need to do so before installing the `arcadiathemeR` package.
```r
# install.packages("remotes")
remotes::install_github("Arcadia-Science/arcadiathemeR")
```

## Usage
See the full vignette (TBD)

To access the functions in the arcadiathemeR package, load with: 
```r
library(arcadiathemeR)
```

The arcadiathemeR package is modeled after the [`ggthemes` package](https://github.com/jrnold/ggthemes), layering on the plot theme and color palettes in the same fashion as the `ggthemes` package. 

```{r, base_use}
library(ggplot2)
library(arcadiathemeR)

ggplot(data=mtcars, aes(x=hp, y=mpg, color=as.factor(cyl))) +
  geom_point(size=2.5) +
  theme_arcadia(x_axis_type = "numerical") +
  scale_color_arcadia("primary")
```

By default the `theme_arcadia()` function assumes that both axes are numerical data. Since we have different font and plot styles for categorical data, you can specify if the axis is categorical with: 

```{r, categorical_plot}
ggplot(data=diamonds, aes(x=cut, fill=cut)) +
  geom_bar() +
  theme_arcadia(x_axis_type = "categorical") +
  scale_fill_arcadia("secondary", reverse = TRUE) +
  scale_y_continuous(expand=c(0,0)) # removes whitespace between axis and bars
```


You can also select different indices of colors from the palettes within the `scale` function:

```{r, scale_index}
ggplot(mtcars, aes(x = hp, fill = as.factor(cyl))) +
  geom_density(alpha = 0.8, color = NA) + # remove border line from filled-in density plots
  theme_arcadia() +
  scale_fill_arcadia("blue_shades", start=2, end=5) +
  scale_y_continuous(expand=c(0,0)) +
  scale_x_continuous(expand=c(0,0)) # remove whitespace between both axes and the plot
```


You can also apply gradient palettes to your plots with `gradient_fill_arcadia` or `gradient_scale_arcadia` in a similar fashion to the above: 
```{r, gradient_example}
ggplot(data = mtcars, aes(x = hp, y = mpg, color = hp)) +
 geom_point(size=2.5) + 
 theme_arcadia() + 
 gradient_color_arcadia("lisafrank")

```
You can view all the color palette options and the individual hex codes composing each palette within the main and gradient palettes with:
```{r}
show_arcadia_palettes()
show_arcadia_gradients()
```

## Development
To install the package locally while in development, follow the instructions [here](https://stackoverflow.com/questions/21171142/how-to-install-r-package-from-private-repo-using-devtools-install-github). Briefly: 

1. Add a `.Renviron` file to the folder where you are going to install this package
2. Create a Github personal access token, select "repo" to access private repositories 
3. Save the token in the `.Renviron` file as `GITHUBTOKEN=<string>`
4. Install from a specific branch with: 
```r
# TODO change to main once deployed
remotes::install_github("Arcadia-Science/arcadiathemeR", \
ref="EAM/palette-updates", \
auth_token=Sys.getenv("GITHUBTOKEN"))
```
